\cvsection{Employment}
\begin{cventries}
  \cventry
      {Software Engineer}
      {Homevest}
      {Tallinn, Estonia / Remote}
      {Feb. 2022 - present}
      {
        \begin{cvitems}
          \item {Building up and maintaining Homevest's platform and integrations.}
        \end{cvitems}
      }
  \cventry
      {Senior Software Engineer, Tech Lead}
      {Wise}
      {Tallinn, Estonia}
      {Sept. 2017 - Dec. 2021}
      {
        \begin{cvitems}
          \item {Maintaining and developing Wise's public API, bank integrations, batch payments and payment dual authorization. Managing a team of eventually 6 developers.}
        \end{cvitems}
      }
  \cventry
    {Software Developer, Project Manager}
    {Concise Systems}
    {Tallinn, Estonia}
    {Jan. 2016 - Apr. 2017}
    {
      \begin{cvitems}
        \item {Working as a software developer, managing subcontractors and acting as a key account manager, participating in recruitment and tender application preparation, minor office IT work.}
      \end{cvitems}
    }
  \cventry
    {Senior Software Developer}
    {CGI Estonia}
    {Tartu, Estonia}
    {Mar. 2015 - Nov. 2015}
    {
      \begin{cvitems}
        \item {Team lead for developing an internal system for SES. Work on-site in Luxembourg.}
      \end{cvitems}
    }
  \cventry
    {Software Developer, Team lead}
    {Concise Systems}
    {Tartu, Estonia}
    {May 2013 - Feb. 2015}
    {
      \begin{cvitems}
        \item {Team lead for developing EasyPark parking permits system.}
      \end{cvitems}
    }
  \cventry
    {Software Developer}
    {Affecto Estonia}
    {Tallinn, Estonia}
    {Jan. 2006 - Mar. 2013}
    {
      \begin{cvitems}
        \item {Various consulting projects}
      \end{cvitems}
    }
  \cventry
    {Internship}
    {Abobase Systems}
    {Tallinn, Estonia}
    {Aug. 2005 - Dec. 2005}
    {
      \begin{cvitems}
        \item {Development of a prototype for an internal ordering system for Hansabank.}
      \end{cvitems}
    }
\end{cventries}
